Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-13 csf-2017/paper.tex
Added question to example section
Math update
Work on related work.

\title{Reasoning about a Capability Machine with Local Capabilities\\
 Provably Safe Stack and Return Pointer Management (without OS Support)}

@@

\section{A capability machine with local capabilities}
In this paper, we work with a formal capability machine that has all the
characteristics of real capability machines, as well as local capabilities much
like CHERI's, but is otherwise kept as simple as possible. It is inspired by
both the M-Machine~\cite{Carter:1994:HSF:195473.195579} and
CHERI~\cite{Watson2015Cheri}. To avoid getting bogged down in uninteresting
detail, we assume an infinite address space and unbounded integers.

@@

@@

\section{Stack and return pointer management using local capabilities}
\label{sec:stack-and-return-pointer}
\lau{Do we want to use the term ``pointer'' at any point? I have also used it, but I guess it might create some confusing to whether we have traditional pointer as well as capabilities?}
One of the contributions in this paper is a demonstration that local
capabilities on a capability machine can be used in a stack and return pointer
management scheme that enforces control flow integrity in a way that is provably
watertight, potentially efficient, does not rely on a trusted central stack
manager, and with support for exposing higher-order interfaces to an adversary.
In this section, we explain this discipline. We start by explaining the
high-level approach, the different issues that need to be taken into account,
starting with first-order interfaces and moving onto a higher-order setting
after that. After that, we define a number of reusable macro-instructions that
can be used to conveniently apply the proposed discipline in subsequent
examples.

@@

Already important is the fact that the return pointer must be provided to the
adversary as a local capability. If not, the adversary would be able to store
away the return pointer in a global data structure, and they would be able to jump
to it in circumstances where this should not be possible: for example, they may
store the return pointer, legally jump to it a first time, wait to be invoked
again and then jump to the old return pointer a second time, rather than the new
return pointer received for the new invocation. Similarly, they may store the
return pointer, invoke a function in our code, wait for us to invoke him again
and then jump to the stored, old return pointer rather than the new one he
received upon the second invocation. \lau{If we need space, then maybe one of the examples is sufficient.}
\lau{In the examples, we refer to the local return pointer as
  ``protected return pointer''. We should either introduce that here
  or use a different formulation in the examples. }

@@

\section{Logical relation}
In order to be able to reason about programs running on the capability
machine and prove properties such as well-bracketedness and
encapsulation about them, we define a unary logical relation.
% Intuition
The logical relation is a semantic model of all the words on the
capability machine that are definitely safe to give to an
adversary. Whether a capability is safe to give to an adversary
depends heavily on the contents of the memory since instructions as well
as capabilities may reside in memory. Hence we index the logical
relation over worlds, which are used to model the memory, and our logical
relation is thus an example of what is often referred to as a Kripke
logical relation. A world consists of a finite set of regions, and each region
can be understood as a protocol describing the possible evolution of
part of the memory. Memory changes during an
execution since new memory can be allocated and part of the existing
memory can change. We use two future world relations to capture
such changes to the memory in our model.
%

@@

\section{Examples}
In this section, we demonstrate how our formal model of capability
safety allows us to prove local state encapsulation and control-flow
integrity properties for challenging program examples. The security
measures of Section~\ref{sec:stack-and-return-pointer} are deployed to
ensure these properties. Since we are dealing with assembly language,
there are many details to the formal treatment, and therefore we
necessarily have to omit some details in the lemmas we state here.
The interested reader can find all the technical details in the
techincal report~\cite{XXX}.

\subsection{Encapsulation of local state}
The capability machine provides encapsulation of local state. The
programs \texttt{f1} in \figurename~\ref{fig:prog-f1} and \texttt{f2}
\figurename~\ref{fig:prog-f2} demonstrate this.  The two programs
\texttt{f1} and \texttt{f2} are very similar. They both store some
local state, call an untrusted piece of code ($\adv$), and then tests
whether the local state is unchanged. They differ in the way they do
this. Program \texttt{f1} assumes it has access to a stack capability
and uses the stack to store its local state. It also uses the
stack-based calling convention \texttt{scall} to call the untrusted code. On the
other hand, \texttt{f2} allocates a new piece of memory for its local
state and uses an activation-record based calling convention
(described in the technical report) to run the adversarial code.

@@

For both programs, we can prove that if they are linked with an
adversary, $\adv$, that is allowed to allocate new memory but
otherwise has no capabilities, then the assertion will never fail when
executing the program (see Lemmas~\ref{lem:correctness-f1}
and~\ref{lem:correctness-f2} below).  \lars{shouldn't we say already
here that the adversary is a global capability and that is why,
intuitively, the local state is preserved ?} \lau{Due to the ``order
of control'', \texttt{f1} runs first. The lemma is quite restrictive
on the adversary in the sense that it only has access to malloc (and
whatever we give et access to). Specifically, it does not have access
to the stack capability and because of that we don't need to check it
first. We could write that the lemmas are limited in their assumptions
to make them simpler and a more complicated example is coming up.}
The two examples also illustrate the versatility of the logical
relation. The two examples use different calling convention, but the
logical relation is not specific to any calling convention, so we can
use it to reason about both programs.

@@

In order to formulate lemmas about \texttt{f1} and \texttt{f2}, we
need a way to observe whether the assertion fails. To this end, we
assume access to a flag (an address in memory). When the assertion
fails, it sets the flag to $1$ and halts. A slightly simplified
version of the correctness lemma for \texttt{f1} is:
\begin{lemma}
  \label{lem:correctness-f1}
  Let
\[
    \begin{array}{r@{}lr@{}l}
    c_{\var{adv}} & \;\defeq ((\entry,\glob),\dots) & c_{\var{stk}} & \;\defeq ((\rwlx,\local),\dots)\\
    c_{f1} & \;\defeq ((\rwx,\glob),\dots) & c_\link &\; \defeq ((\readonly,\glob),\dots)\\
    c_\malloc &\; \defeq ((\entry,\glob),\dots) & \reg& \; \in \Regs \\
    m &  \multicolumn{3}{@{}l}{\;\defeq \ms_{f1} \uplus \ms_\flag \uplus \ms_{\var{link}} \uplus \hs_\adv \uplus \ms_{\malloc} \uplus} \\
      & \multicolumn{3}{@{}l}{\phantom{\;\defeq \;}  \ms_{\var{stk}} \uplus \ms_{\var{frame}}} \\
    \end{array}
\]
  where each of the capability has an appropriate range of authority and pointer and
  \begin{itemize}
  \item $\ms_{f1}$ contains $c_\link$, $c_\flag$ and the code of \texttt{f1}
  \item $\ms_\flag(\flag) = 0$
  \item $\ms_{\var{link}}$ contains $c_\adv$ and $c_\malloc$
  \item $\hs_\adv$ contains $c_\link$ and otherwise only instructions.
  \end{itemize}
  If $(\reg\update{\pcreg}{c_{f1}}\update{r_\stk}{c_\stk},m) \step^* (\halted,m')$,
  then $m'(\flag) = 0$
\end{lemma}

@@

\lau{in the following paragraph, we could make a reference to
  \textbf{invoking the adversary} from
  section~\ref{sec:stack-and-return-pointer} where the problem is
  first introduced. In fact, this paragraph is a reiteration of the
  problem in the aformentioned section.}
In \texttt{f3} there are two calls to an adversary and in order for
the assertion in the middle to succeed, they need to be
well-bracketed. If the adversary is able to store the protected return
pointer from the first call, so it is available for the second call, then it can be used
in a context where \texttt{f3} has $2$ on top of its stack which will cause the
assertion to fail. The protected return pointer is passed as a local
capability, so the only means the adversary has to store it is the
stack capability. The stack capability itself is a local capability,
so the adversary can only store it on the stack. This means that after
the adversary jumps to the protected return pointer, \texttt{f3} can
revoke it (by erasing it which happens as part of the
\texttt{scall}). In other words, the adversary cannot store the
protected return pointer for the second call, and it is possible to
prove that the assertion never fails.
\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
f3: push 1
    fetch $r_1$ $\adv$
    scall $r_1$($[]$,$[r_1]$)
    pop $r_2$
    assert $r_2$ 1
    push 2
    scall $r_1$($[]$,$[]$)
    halt
\end{lstlisting}
  \caption{Simple program that relies on control-flow integrity.}
  \label{fig:prog-f3}
\end{figure}

\begin{lemma}
  \label{lem:correctness-f3}
  Making similar assumptions about capabilities and linking as in
  Lemma~\ref{lem:correctness-f1}
  if $(\reg\update{\pcreg}{c_{f3}}\update{r_\stk}{c_\stk},m) \step^*
  (\halted,m')$, then $m'(\flag) = 0$.
\end{lemma}

The final example, in \figurename~\ref{fig:prog-g1}, is a faithful
translation of a trciky example known from the
litterature\cite{XXX}. It consists of two parts, \texttt{g1} and
\texttt{f4}. \texttt{g1} is a closure generator that generates
closures with one variable $x$ set to $0$ in its environment and
\texttt{f4} as the program. The program \texttt{f4} expects two
arguments: a stack and a callback. The stack is necessary to use
\texttt{scall}, but because it comes from an untrusted source, we need
to make sure that it has the correct permission and fits with our
stack dicipline. The callback must be global for the program to work,
we will get back to this point. The program now sets $x$ to $0$ and
calls the callback. When it returns from the callback, it sets $x$ to
$1$ and calls the callback a second time. When it returns from the
callback, it asserts $x$ is $1$ and returns.

To illustrate how subtle this program is, consider one way an
adversary may try to make the assertion fail. In the second callback
an adversary can get to the first callback by calling the closure one
more time. If the adversary can save the protected return pointer in
the second callback and use it in the first, then the assertion will
fail because $x$ is $0$ before the first callback. The protected return
pointer cannot be transfered between the callbacks, so this does not
work.

\begin{lemma}
  \label{lem:correctness-g1}
  Making similar assumptions about capabilities and linking as in
  Lemma~\ref{lem:correctness-f1} 
  if
  \[
  (\reg_0\update{\pcreg}{c_\adv}\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}},m) \step^* (\halted,m'),
  \]
  then $m'(\flag) = 0$.
\end{lemma}

@@

Cap-mach:
\begin{itemize}
\item \cite{Watson2015Cheri} CHERI papers
\item \cite{akram_el-korashy_formal_2016}
\end{itemize}

Logical relation:
\begin{itemize}
\item \cite{Hur:2011:KLR:1926385.1926402}
\item \cite{Dreyer:jfp12}
\item \cite{Devriese:2016ObjCap}
\item \cite{osvald_gentrification_2016}
\end{itemize}

Other papers that enforce well-bracketed control flow at low level (using a
trusted stack manager)
\begin{itemize}
\item \cite{patrignani_modular_2016-1}
\item \cite{juglaret_beyond_2016-1}
\item other stuff?
\end{itemize}

>>>>

\title{Reasoning about a Capability Machine with Local Capabilities\\
 Provably Safe Stack and Return Pointer Management (without OS Support).}

@@

\section{A capability machine with local capabilities}
\label{sec:capab-mach-with}
In this paper, we work with a formal capability machine that has all the
characteristics of real capability machines, as well as local capabilities much
like CHERI's, but is otherwise kept as simple as possible. It is inspired by
both the M-Machine~\cite{Carter:1994:HSF:195473.195579} and
CHERI~\cite{Watson2015Cheri}. To avoid getting bogged down in uninteresting
detail, we assume an infinite address space and unbounded integers.

@@

We point out that our local capabilities capture only a part of the semantics of
local capabilities in CHERI. Specifically, on top of the above restrictions,
CHERI's default implementation of CCall additionally forbids local capabilities
from being passed accross module boundaries, something which we rely on
crucially in this paper, for passing around local return pointers and stack
capabilities. However, CHERI's CCall is not implemented in hardware, but in
software, precisely to allow experimenting with alternative models like ours.

@@

\section{Stack and return pointer management using local capabilities}
\lau{Do we want to use the term ``pointer'' at any point? I have also used it, but I guess it might create some confusing to whether we have traditional pointer as well as capabilities?}
One of the contributions in this paper is a demonstration that local
capabilities on a capability machine can be used in a stack and return pointer
management scheme that enforces control flow integrity in a way that is provably
watertight, potentially efficient, does not rely on a trusted central stack
manager, and with support for exposing higher-order interfaces to an adversary.
In this section, we explain this discipline. We start by explaining the
high-level approach, the different issues that need to be taken into account,
starting with first-order interfaces and moving onto a higher-order setting
after that. After that, we define a number of reusable macro-instructions that
can be used to conveniently apply the proposed discipline in subsequent
examples.

@@

Already important is the fact that the return pointer must be provided to the
adversary as a local capability. If not, the adversary would be able to store
away the return pointer in a global data structure, and they would be able to jump
to it in circumstances where this should not be possible: for example, they may
store the return pointer, legally jump to it a first time, wait to be invoked
again and then jump to the old return pointer a second time, rather than the new
return pointer received for the new invocation. Similarly, they may store the
return pointer, invoke a function in our code, wait for us to invoke him again
and then jump to the stored, old return pointer rather than the new one he
received upon the second invocation. \lau{If we need space, then maybe one of the examples is sufficient.}

@@

\section{Logical relation}
\label{sec:logical-relation}
In order to be able to reason about programs running on the capability
machine and prove properties such as well-bracketedness and
encapsulation about them, we define a unary logical relation.
% Intuition
The logical relation is a semantic model of all the words on the
capability machine that are definitely safe to give to an
adversary. Whether a capability is safe to give to an adversary
depends heavily on the contents of the memory since instructions as well
as capabilities may reside in memory. Hence we index the logical
relation over worlds, which are used to model the memory, and our logical
relation is thus an example of what is often referred to as a Kripke
logical relation. A world consists of a finite set of regions, and each region
can be understood as a protocol describing the possible evolution of
part of the memory. Memory changes during an
execution since new memory can be allocated and part of the existing
memory can change. We use two future world relations to capture
such changes to the memory in our model.
%

@@

\section{Examples}
In this section, we demonstrate how our formal model of capability
safety allows us to prove local state encapsulation and control-flow
integrity properties for challenging examples. 
Since we are dealing with assembly language, 
there are many details to the formal treatment , and therefore we 
necessarily have to omit some details
in the lemmas we state here.  The interested reader can find all the
technical details in the techincal report~\cite{XXX}.

\subsection{Encapsulation of local state}
The capability machine provides encapsulation of local state. The
programs \texttt{f1} in \figurename~\ref{fig:prog-f1} and 
\texttt{f2} \figurename~\ref{fig:prog-f2} demonstrate this.
The two programs \texttt{f1} and \texttt{f2} are very similar. They both
store some local data, call an untrusted piece of code ($\adv$), and
then tests whether local state is unchanged. They differ in the way
they do this. Program \texttt{f1} assumes it has access to a stack capability
and uses the stack to store its local state. It also uses the
stack-based calling convention to call the untrusted code. On the
other hand, \texttt{f2} allocates a new piece of memory for its local
state and uses an activation-record based calling convention
(described in the technical report) to run the adversarial code.

@@

For both programs, we can prove that if they are linked with an
adversary, $\adv$, that is allowed to allocate new memory but otherwise has no
capabilities, then the assertion will never fail when
executing the program (see Lemmas~\ref{lem:correctness-f1}
and~\ref{lem:correctness-f2} below).
\lars{shouldn't we say already here that the adversary is a global 
  capability and that is why, intuitively, the local state is
  preserved ?}
The two examples also illustrate
the versatility of the logical relation. The two examples use
different calling convention, but the logical relation is not specific
to any calling convention, so we can use it to reason about both
programs.

@@

In order to formulate lemmas about \texttt{f1} and \texttt{f2}, we
need a way to observe whether the assertion fails. To this end, we
assume access to a flag (an address in memory)
which will be set to $1$ by the assertion if it
fails. A slightly simplified version of the correctness lemma for
\texttt{f1} is:
\begin{lemma}
  \label{lem:correctness-f1}
  Let
\[
    \begin{array}{r@{}lr@{}l}
    c_{\var{adv}} & \;\defeq ((\entry,\glob),\dots) & c_{\var{stk}} & \;\defeq ((\rwlx,\local),\dots)\\
    c_{f1} & \;\defeq ((\rwx,\glob),\dots) & c_\link &\; \defeq ((\readonly,\glob),\dots)\\
    c_\malloc &\; \defeq ((\entry,\glob),\dots) & & \\
    m &  \multicolumn{3}{@{}l}{\;\defeq \ms_{f1} \uplus \ms_\flag \uplus \ms_{\var{link}} \uplus \hs_\adv \uplus \ms_{\malloc} \uplus} \\
      & \multicolumn{3}{@{}l}{\phantom{\;\defeq \;}  \ms_{\var{stk}} \uplus \ms_{\var{frame}}} \\
    \end{array}
\]
  where each of the capability has an appropriate range of authority and pointer and
  \begin{itemize}
  \item $\ms_{f1}$ contains $c_\link$, $c_\flag$ and the code of \texttt{f1}
  \item $\ms_\flag(\flag) = 0$
  \item $\ms_{\var{link}}$ contains $c_\adv$ and $c_\malloc$
  \item $\hs_\adv$ contains $c_\link$ and otherwise only instructions.
  \end{itemize}
  If $(\reg\update{\pcreg}{c_{f1}}\update{r_\stk}{c_\stk},m) \step^* (\halted,m')$,
  then $m'(\flag) = 0$
\end{lemma}

@@

In \texttt{f3} there are two calls to an adversary and in order for
the assertion in the middle to succeed, they need to be
well-bracketed. If the adversary is able to store the protected return
pointer, so it is available for the second call, then it can be used
in a context where \texttt{f3} has 2 on top of its stack which will cause the
assertion to fail. The protected return pointer is passed as a local
capability, so the only means the adversary has to store it is the
stack capability. The stack capability itself is a local capability,
so the adversary can only store it on the stack. This means that after
the adversary jumps to the protected return pointer, \texttt{f3} can
revoke it (by overwritting it which happens as part of the
\texttt{scall}). In other words, the adversary cannot store the
protected return pointer for the second call, and it is possible to
prove that the assertion never fails.
\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
f3: push 1
    fetch $r_1$ $\adv$
    scall $r_1$($[]$,$[r_1]$)
    pop $r_2$
    assert $r_2$ 1
    push 2
    scall $r_1$($[]$,$[]$)
    halt
\end{lstlisting}
  \caption{Simple program that relies on control-flow integrity.}
  \label{fig:prog-f3}
\end{figure}

\begin{lemma}
  \label{lem:correctness-f3}
  Making similar assumptions about capabilities and linking as in
  Lemma~\ref{lem:correctness-f1} but assuming no stack capability
  if $(\reg\update{\pcreg}{c_{f3}}\update{r_\stk}{c_\stk},m) \step^*
  (\halted,m')$, then $m'(\flag) = 0$.
\end{lemma}

The final example, in \figurename~\ref{fig:prog-g1}, is a faithful
translation of a trciky example known from the
litterature\cite{XXX}. It consists of two parts, \texttt{g1} and
\texttt{f4}. \texttt{g1} is a closure generator that generates a
closure with one variable $x$ set to 0 in its environment and \texttt{f4} as
the program. The program \texttt{f4} expects to arguments: a stack and
a callback. The stack is necessary to use \texttt{scall}, but because
it comes from an untrusted source, we need to make sure that it has
the correct permission and fits with our stack dicipline. The callback
must be global for the program to work, we will get back to this
point. The program now sets $x$ to 0 and calls the callback. When it
returns from the callback, it sets $x$ to 1 and calls the callback a
second time. When it returns from the callback, it asserts $x$ is 1
and returns.

To illustrate how subtle this program is, consider one way an
adversary may try to make the assertion fail. In the second callback
an adversary can get to the first callback by calling the closure one
more time. If the adversary can save the protected return pointer in
the second callback and use it in the first, then the assertion will
fail because $x$ is 0 before the first callback. The protected return
pointer cannot be transfered between the callbacks, so this does not
work.

\begin{lemma}
  \label{lem:correctness-g1}
  Making similar assumptions about capabilities and linking as in
  Lemma~\ref{lem:correctness-f1} but assuming no stack capability
  if
  \[
  (\reg_0\update{\pcreg}{c_\adv}\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}},m) \step^* (\halted,m'),
  \]
  then $m'(\flag) = 0$.
\end{lemma}

@@

Capability machines originate with Dennis and Van
Horn~\cite{Dennis:1966:PSM:365230.365252} and we refer to
\citet{Levy1984capability} and \citet{Watson2015Cheri} for an overview of
previous work in the area. The capability machine formalised in
Section~\ref{sec:capab-mach-with} is a simple but representative model, modeled
mainly after the M-Machine~\cite{Carter:1994:HSF:195473.195579} (the enter
pointers resemble the M-Machine's) and
CHERI~\cite{Watson2015Cheri,Woodruff:2014:CCM:2665671.2665740} (the memory
capabilities resemble CHERI's). The latter is a recent and relatively mature
capability machine, which combines capabilities with a virtual memory approach,
in the interest of backwards compatibility and gradual adoption. Our local
capabilities are inspired by CHERI's, although as discussed, they can be passed
accross module boundaries, contrary to what is enforced by CHERI's default CCall
implementation.

We believe local capabilities

Other papers that enforce well-bracketed control flow at low level (using a
trusted stack manager)
\begin{itemize}
\item \cite{patrignani_modular_2016-1}
\item \cite{juglaret_beyond_2016-1}
\item other stuff?
\end{itemize}
CFI: 
\begin{itemize}
\item \cite{budiu_architectural_2006,abadi_control-flow_2005}
\end{itemize}

Our logical relation is a unary, step-indexed Kripke logical relation (SKLR)
with recursive
worlds~\cite{Appel:2001:IMR:504709.504712,Ahmed2004semantics,Birkedal:2011:SKM:1926385.1926401},
closely related to the one used by \citet{Devriese:2016ObjCap} to formulate
capability-safety in a high-level JavaScript-like lambda calculus. Our
fundamental theorem is similar to theirs and can be seen as a formulation of
capability-safety of the capability-machine. Because we are not interested in an
externally observable notion of side-effects (like console output or memory
access traces), we do not require their notion of effect parametricity.

The idea of applying SKLRs to an assembly language was applied before by
\citet{Hur:2011:KLR:1926385.1926402}, who constructed a binary SKLR for
formulating and proving correctness of an ML-to-assembly compiler. Their
condition on the assembly code are quite loose (for example, they allow
hand-written and self-modifying assmebly code), but they do assume code that it
is non-adversarial and respects the ABI of the high-level language (for example,
the code does not store return pointers and invoke them after their intended
lifetime). As a result, they can treat return pointers as evaluation contexts in
a lambda calculus and use biorthogonality~\cite{pitts_higher_1998}. This means
that they define the logical relation to accept evaluation contexts if they
produce related observations for related values and to accept terms if they
produce related observations when plugged into related evaluation contexts. In
our setting, there is no guarantee that adversarial code will treat return
pointers as intended, so, as described in Section~\ref{sec:logical-relation}, we
define our logical in a (arguably natural but still) novel way, using a single
orthogonal closure, i.e. accept terms if they produce related observations when
given related arguments, where those arguments include the return pointer.

Another novel aspect of our logical relation is how we model the temporary
nature of local capabilities. The main insight is that the temporary, revokable
nature of these capabilities can be seen as a generalisation of the special
status of evaluation contexts in lambda calculi. Closely related here is a study
by \citet{Dreyer:jfp12} (DNB) of the impact of higher-order state and control
effects on local relational reasoning. DNB formally capture this special status
of evaluation contexts using Kripke worlds with public and private future world
relations. Our public and private worlds are inspired by theirs and they are at
times remarkably similar. For example, the state-transitition system in the
proof of our assembly version of the awkward example, is exactly the same as the
one used by DNB for the original awkward example. Nevertheless, there are also
remarkable differences: in DNB's logical relation, public future worlds only
turn up in the continuation relation (which we do not have, see above). This is
different from our value relation which uses public and private future worlds
depending on the locality of the capability at hand. Additionally, our worlds
are a bit more complex because, to allow store-local capabilities, they can have
temporary regions that are only monotonous w.r.t. public future worlds, while
DNB's worlds are entirely permanent.

As a side note: our model of local/global capabilities may also be applicable
for reasoning about related ideas in higher-level languages. Specifically,
\citet{osvald_gentrification_2016}'s second-class or local values in Scala are
remarkably similar to the local capabilities we study and we expect they will
support similar reasoning patterns.

\begin{itemize}
\item \cite{akram_el-korashy_formal_2016}
\end{itemize}
